Databrary: A digital data library for sharing research video

### 2015-01-15 jcdl-15/paper.tex
Some intro sentences

>>>>

Video plays a key role in many areas of human research, particularly in developmental psychology, education, ...
Unfortunately, in standard practice, due largely to the perceived burdens of ethics and privacy restrictions, the use of these data is isolated to the researchers who collected them.
The goal of the Databrary project establish policies and tools to allow video data to be documented, organized, and shared so that other researchers can discover and re-purpose existing videos for their own research interest.
Accordingly, Databrary, with developmental psychology as a use case, has created a web-based library and organizational structures to accommodate existing video data, capture contextual information necessary for re-use, and standardize across datasets without placing undue burden on data contributors.
